 

### 2021-07-12 vertical-thermal-review.Rmd
small changes

Leaf metabolism is strongly shaped by $T_{leaf}$, and by the traits and environmental drivers reviewed above, all of which vary across vertical forest gradients (Fig. `r fig_schematic`). 
However, as we detail below, very few studies have valued temperature responses of leaf metabolic rates along a vertical canopy gradient, or compared sun and shade leaves (Table `r table_leaf_metabolism`).

@@

**Differences across forest vertical gradients in biophysical conditions, plant traits, and metabolism and its thermal responses scale up to affect whole-tree ecology and ecosystem ecology.**

Vertical gradients in the biophysical environment shape which plant strategies, or sets of traits, are competitive in understory versus canopy conditions.

>>>>

Leaf metabolism is strongly shaped by $T_{leaf}$, and by the traits and environmental drivers reviewed above, all of which vary across vertical forest gradients (Fig. `r fig_schematic`). 
However, as we detail below, very few studies have evaluated temperature responses of leaf metabolic rates along a vertical canopy gradient, or compared sun and shade leaves (Table `r table_leaf_metabolism`).

@@

**Differences across forest vertical gradients in biophysical conditions, plant traits, and metabolism scale up to affect whole-tree ecology, ecosystem ecology, and their thermal sensitivity (Fig. `r fig_schematic`).** 
Vertical gradients in the biophysical environment shape which plant strategies, or sets of traits, are competitive in canopy versus understory conditions, thereby
